PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-06 paper/sec-results.tex
fixed typo

\paragraph{Drell--Yan lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
energy of \SI{7}{\tera\electronvolt} in the high-mass region
($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
We also select the distributions, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
section~\ref{sec:pineappl-example}, 
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
Mixed-coupling QCD-EW corrections occur only at NNLO, and are therefore not
considered here. EW corrections for this process were computed in
refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
from 12 (34) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
$\mathcal{O}(\alphas^2\alpha)$.
We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
EW corrections for this process
were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
6 (36) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

\paragraph{Z-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
included in any PDF determination, its expected impact on parton densities has been studied in 
ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with the LO and NLO EW corrections,
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 100 (165) parton luminosities,
see appendix~\ref{app:lumis} for details.

>>>>

\paragraph{Drell--Yan lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
energy of \SI{7}{\tera\electronvolt} in the high-mass region
($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
We also select the distributions, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
section~\ref{sec:pineappl-example}, 
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
Mixed-coupling QCD-EW corrections occur only at NNLO, and are therefore not
considered here. EW corrections for this process were computed in
refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_\mathrm{T}^\mathrm{t}$, or the invariant mass of the top-quark
pair, $m_{\mathrm{t}\bar{\mathrm{t}}}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml} (see
also refs.~\cite{Pagani:2016caq,Czakon:2017wor} for studies related to the photon density) and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives
pure QCD contributions at LO, $\mathcal{O}(\alphas^2)$, and
at NLO, $\mathcal{O}(\alphas^3)$. They make up our NLO QCD
computation. The NLO QCD+EW computation includes the $\mathcal{O}(\alphas^2)$
and $\mathcal{O}(\alphas^3)$ QCD contributions, the LO contribution
$\mathcal{O}(\alphas\alpha)$ and the NLO contribution
$\mathcal{O}(\alphas^2\alpha)$.
We do not consider the LO contribution $\mathcal{O}(\alpha^2)$ nor the
NLO contributions $\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$, which have been shown to be negligible~\cite{Czakon:2017wor,Frederix:2018nkq}.
EW corrections for this process
were computed in refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
7 (37) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

\paragraph{Z-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
included in any PDF determination, its expected impact on parton densities has been studied in 
ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with the LO and NLO EW corrections,
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis} for details.
